Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-05-23 ms.qmd
Note

>>>>

  # Now, lets do this but for each habitat, the good old fashioned way. I think that these are so variable because the expected change in the future is quite dramatic, so the variability is high.
  mean_perc_habitat <-  lapply(split(all_pred2_no_sum2,  all_pred2_no_sum2$habitat), function(x) apply(x[,paste0("perc", c(1:3200))], 2, mean, na.rm = TRUE))
  lapply(mean_perc_habitat, mean)
  lapply(mean_perc_habitat, function(x) quantile(x, c(0.025, 0.975)))
  #lapply(mean_perc_habitat, hist)
